Verifying Demonstrations

### 2020-02-26 paper/DB-Schnorr-UWB.tex
Perfects the SimTF UWB proof
Includes the advantage and that it's negligible in the main TF theorem.

\daniel{Work in progress!}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} = 0\).
\end{theorem}

@@

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover without tainting the 
  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
  provided by the prover must be independent from the chosen challenge.
  Now \(\adv\) will provide a correct response with probability~\(p_{\adv}\).
  Hence, \(p_{\S} = p_{\adv}\).
\end{proof}

>>>>

\daniel{Work in progress!}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \frac{1}{m^n}\).
\end{theorem}

@@

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover without tainting the 
  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
  provided by the prover must be independent from the chosen challenge.
  Now \(\adv\) will again provide a correct response with 
  probability~\(p_{\adv}\).

  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
  \(m p_{\adv}\) responses.
  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
  correct responses and, thus, \(p_{\S} = 1\) for any successive 
  authentication.
  This would also make \(p_{\adv} = 1\).
  This contradicts that the secret is not leaked.
  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
  secret leaks.
  This makes the \ac{DBTF} advantage negligible.
\end{proof}
